---
title: "IntentionBehaviorGap"
author: "Yejin Hwang"
date: "3/7/2019"
output: pdf_document
---

```{r}
library(tidyverse)
library(haven) #haven is part of tidyverse, but for some reason, this is needed.
library(ggplot2)
library(cowplot)
library(stargazer)
data1 <- read_dta("./data/final_data1.dta")
data2 <- read_dta("./data/final_data2.dta")
data3 <- read_dta("./data/final_data3.dta")
```

## Recreating Table 2
```{r table2}
# Read in data file, assign to MyData
MyData <- data1

# Select variables in Table 2 from MyData, put in dataframe d
vars <- c(34, 35, 36, 51, 52)
d <- data1[,vars]
 
# Compute means without missing (NA) values
summary(d)
sapply(d, mean, na.rm=TRUE)
sapply(d, sd, na.rm=TRUE)
```

```{r}
stargazer(data.frame(d), title = "Table 2—Action-Plan Descriptives", omit.summary.stat = c("min", "max", "p25", "p75"), type="text")
```

```{r}
goal_opport <- data1$goal_opport[!is.na(data1$goal_opport)]
goal_submit <- data1$goal_submit[!is.na(data1$goal_submit)]
goal_hours <- data1$goal_hours[!is.na(data1$goal_hours)]
activity_days <- data1$activity_days[!is.na(data1$activity_days)]
APcomplete <- data1$APcomplete[!is.na(data1$APcomplete)]

rownames <- c("Completed AP", "Activity days", "Goal: Job search hours", "Goal: Opportunities to identify", "Goal: Applications to submit")
observations <- c(length(APcomplete), length(activity_days), length(goal_hours), length(goal_opport), length(goal_submit))
mean <- c(mean(APcomplete), mean(activity_days), mean(goal_hours), mean(goal_opport), mean(goal_submit))
sd <- c(sd(APcomplete), sd(activity_days), sd(goal_hours), sd(goal_opport), sd(goal_submit))

table2_brute_force <- data.frame(rownames, observations, mean, sd)
table2_brute_force
```


Note:
windsorized: how they deal with wacky means / outliers
i.e. using x9 to replace x10
use windsor.mean function
may be prewindsorized data


Tables:
```{r table1}
controlGroup <- data1 %>% select(age_yr, female_d, educ_yr, bs_b15a,moved_yesno_d,bs_b1_ever_job_d,bs_b13_reserv_wage,bs_b14,bs_transport_cost,bs_b16,bs_c2,bs_c3)
stargazer::stargazer(data.frame(controlGroup), summary.stat = c("n", "mean", "median", "sd"), type = "text", title = "Table 1—Sample Characteristics")
```

summary stats: tables 1 and 2
Table 3-Effects on Job Search Intensity. panel-data regression and se. outcome var winsorized=remove extreme values
Table 4-Effects on Employment Outcomes. regression and se.
Table 5-Effects on Frequency of Search-Channel Use

Graphs:
Figure 1. Intention-Behavior Gap: Difference at Baseline - density plot Hours and apps difference: Goal - Baseline

```{r figure1}
hours_diff_density <- ggplot(data1, aes(hours_diff, stat(density))) + geom_histogram(fill = "#416b85", bins = 18) + labs(x = "Hours difference: Goal - Baseline", y = "Density") + ylim(0, 0.15)
apps_diff_density <- ggplot(data1, aes(apps_diff, stat(density))) + geom_histogram(fill = "#416b85", bins = 18) + labs(x = "Apps difference: Goal - Baseline", y = "Density")
plot_grid(hours_diff_density, apps_diff_density)
ggsave("figure1.jpg")
```

Table 5
```{r}
#data2
#b1_1_t: Empl. agency
#b1_2_t: dropped cv
#b1_3_t: placed ad
#b1_4_t: answered ad
#b1_5_t: searched online
#b1_6_t: Fam./Friends
#b4_t: employer responses

m1_t5 <- lm(b1_1_t ~ ws_d + ws_plus_d + educ_yr + age_yr + female_d + bs_b15a + lang_xhosa_d + lang_venda_d + lang_zulu_d + nomiss_bs_c1_1 + missd_bs_c1_1 + as.factor(location_f) + as.factor(round), data = data2)
m2_t5 <- lm(b1_2_t ~ ws_d + ws_plus_d + educ_yr + age_yr + female_d + bs_b15a + lang_xhosa_d + lang_venda_d + lang_zulu_d + nomiss_bs_c1_2 + missd_bs_c1_2 + as.factor(location_f) + as.factor(round), data = data2)
m3_t5 <- lm(b1_3_t ~ ws_d + ws_plus_d + educ_yr + age_yr + female_d + bs_b15a + lang_xhosa_d + lang_venda_d + lang_zulu_d + nomiss_bs_c1_3 + missd_bs_c1_3 + as.factor(location_f) + as.factor(round), data = data2)
m4_t5 <- lm(b1_4_t ~ ws_d + ws_plus_d + educ_yr + age_yr + female_d + bs_b15a + lang_xhosa_d + lang_venda_d + lang_zulu_d + nomiss_bs_c1_4 + missd_bs_c1_4 + as.factor(location_f) + as.factor(round), data = data2)
m5_t5 <- lm(b1_5_t ~ ws_d + ws_plus_d + educ_yr + age_yr + female_d + bs_b15a + lang_xhosa_d + lang_venda_d + lang_zulu_d + nomiss_bs_c1_5 + missd_bs_c1_5 + as.factor(location_f) + as.factor(round), data = data2)
m6_t5 <- lm(b1_6_t ~ ws_d + ws_plus_d + educ_yr + age_yr + female_d + bs_b15a + lang_xhosa_d + lang_venda_d + lang_zulu_d + nomiss_bs_c1_6 + missd_bs_c1_6 + as.factor(location_f) + as.factor(round), data = data2)
stargazer(m1_t5, m2_t5, m3_t5, m4_t5, m5_t5, m6_t5, colnames = FALSE, column.labels = c("Empl. agency", "Dropped CV", "Placed ad", "Answered ad", "Searched online", "Fam./friends"), keep = c("ws_d", "ws_plus_d"), keep.stat =c("n","rsq"), type = "text", supress.errors = TRUE, title="Table 5—Effects on Frequency of Search-Channel Use", add.lines = list(c("p-value", "0.0047**", "0.001101**", "0.4906", "0.001291**", "0.0009031***", "0.7577")))

#stargazer type = latex
```

```{r}
#summary mod
library(car)
linearHypothesis(m1_t5, c("ws_d = ws_plus_d"))
```

```{r}
linearHypothesis(m2_t5, c("ws_d = ws_plus_d"))
```

```{r}
linearHypothesis(m3_t5, c("ws_d = ws_plus_d"))
```

```{r}
linearHypothesis(m4_t5, c("ws_d = ws_plus_d"))
```

```{r}
linearHypothesis(m5_t5, c("ws_d = ws_plus_d"), singular.ok = TRUE)
```

```{r}
linearHypothesis(m6_t5, c("ws_d = ws_plus_d"), singular.ok = TRUE)
```

```{r}

```


