---
title: "IntentionBehaviorGap"
author: "Yejin Hwang"
date: "3/7/2019"
output: pdf_document
---

```{r}
library(tidyverse)
library(haven) #haven is part of tidyverse, but for some reason, this is needed.
library(ggplot2)
library(cowplot)
data1 <- read_dta("./data/final_data1.dta")
data2 <- read_dta("./data/final_data2.dta")
data3 <- read_dta("./data/final_data3.dta")
```

Tables:
summary stats: tables 1 and 2
Table 3—Effects on Job Search Intensity. panel-data regression and se. outcome var winsorized=remove extreme values
Table 4—Effects on Employment Outcomes. regression and se.
Table 5—Effects on Frequency of Search-Channel Use

Graphs:
Figure 1. Intention-Behavior Gap: Difference at Baseline - density plot Hours and apps difference: Goal − Baseline

```{r}
hours_diff_density <- ggplot(data1, aes(hours_diff, stat(density))) + geom_histogram(fill = "#416b85", bins = 18) + labs(x = "Hours difference: Goal − Baseline", y = "Density") + ylim(0, 0.15)
apps_diff_density <- ggplot(data1, aes(apps_diff, stat(density))) + geom_histogram(fill = "#416b85", bins = 18) + labs(x = "Apps difference: Goal − Baseline", y = "Density")
plot_grid(hours_diff_density, apps_diff_density)
```

Table 3:

```{r}

#TABLE3

first <- lm(b2_t ~ ws_d + ws_plus_d + nomiss_bs_c2 + missd_bs_c2 + as.factor(location_f) + as.factor(round), data = final_data2)
summary(first)

second <- lm(b2_t ~ ws_d + ws_plus_d + nomiss_bs_c2 + missd_bs_c2 +
               educ_yr + age_yr + female_d + bs_b15a + lang_xhosa_d + lang_venda_d + lang_zulu_d +
               as.factor(location_f) + as.factor(round), data = final_data2)
summary(second)

third <- lm(b3_t ~ ws_d + ws_plus_d + nomiss_bs_c3 + missd_bs_c3 + as.factor(location_f) + as.factor(round), data = final_data2)
summary(third)

fourth <- lm(b3_t ~ ws_d + ws_plus_d + nomiss_bs_c3 + missd_bs_c3 +
               educ_yr + age_yr + female_d + bs_b15a + lang_xhosa_d + lang_venda_d + lang_zulu_d +
               as.factor(location_f) + as.factor(round), data = final_data2)
summary(fourth)

#use stargazer to exclude variables
#na.rm=TRUE
```

Table 3:

```{r}

#TABLE4

one <- lm(b4_t ~ ws_d + ws_plus_d + nomiss_bs_c4 + missd_bs_c4 + as.factor(location_f) + as.factor(round), data = final_data2)
summary(one)

two <- lm(b4_t ~ ws_d + ws_plus_d + nomiss_bs_c4 + missd_bs_c4 +
            educ_yr + age_yr + female_d + bs_b15a +
            lang_xhosa_d + lang_venda_d + lang_zulu_d +
            as.factor(location_f) + as.factor(round), data = final_data2)
summary(two)

three <- lm(b6_t ~ ws_d + ws_plus_d + nomiss_bs_c6 + missd_bs_c6 + 
              as.factor(location_f) + as.factor(round), data = final_data2)
summary(three)
  

four <- lm(b6_t ~ ws_d + ws_plus_d + nomiss_bs_c6 + missd_bs_c6 +
             educ_yr + age_yr + female_d + bs_b15a +
             lang_xhosa_d + lang_venda_d + lang_zulu_d +
             as.factor(location_f) + as.factor(round), data = final_data2)
summary(four)


five <- lm(a1_t ~ ws_d + ws_plus_d +
             as.factor(location_f) + as.factor(round), data = final_data2)
summary(five)
  

six <- lm(a1_t ~ ws_d + ws_plus_d + educ_yr + age_yr + female_d + bs_b15a +
            lang_xhosa_d + lang_venda_d + lang_zulu_d +
            as.factor(location_f) + as.factor(round), data = final_data2)
summary(six)
```

