---
title: "IntentionBehaviorGap"
author: "Yejin Hwang"
date: "3/7/2019"
output: pdf_document
---

```{r}
library(tidyverse)
library(haven) #haven is part of tidyverse, but for some reason, this is needed.
library(ggplot2)
library(cowplot)
#Run this: (if error is here^)
#install.packages("cowplot")
data1 <- read_dta("./data/final_data1.dta")
data2 <- read_dta("./data/final_data2.dta")
data3 <- read_dta("./data/final_data3.dta")
```

# Recreating Table 2

```{r}

# Read in data file, assign to MyData
MyData <- final_data1

# Select variables in Table 2 from MyData, put in dataframe d
vars <- c(34, 35, 36, 51, 52)
d <- MyData[,vars]
 
# Compute means without missing (NA) values
summary(d)
sapply(d, mean, na.rm=TRUE)
sapply(d, sd, na.rm=TRUE)

```

Tables:
summary stats: tables 1 and 2
Table 3—Effects on Job Search Intensity. panel-data regression and se. outcome var winsorized=remove extreme values
Table 4—Effects on Employment Outcomes. regression and se.
Table 5—Effects on Frequency of Search-Channel Use

Graphs:
Figure 1. Intention-Behavior Gap: Difference at Baseline - density plot Hours and apps difference: Goal − Baseline

```{r}
hours_diff_density <- ggplot(data1, aes(hours_diff, stat(density))) + geom_histogram(fill = "#416b85", bins = 18) + labs(x = "Hours difference: Goal − Baseline", y = "Density") + ylim(0, 0.15)
apps_diff_density <- ggplot(data1, aes(apps_diff, stat(density))) + geom_histogram(fill = "#416b85", bins = 18) + labs(x = "Apps difference: Goal − Baseline", y = "Density")
plot_grid(hours_diff_density, apps_diff_density)
>>>>>>> 9095e35b2acf2f460dcb3a7c79127be07cab05ff
```
